### 2018-12-15 Paper/Envelopes.tex
Updated paper

\begin{figure}[htbp]
\centering
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
set grid
set key above
set xr [-2:2]
set yr [-0.75:0.75]
set xl '$T$'
set xtics 1

unset key
set multiplot layout 1, 2

set size 0.5, 1
p '../Stable/Envelope8.dat' u 1:4 w l t 'Magnitude', \
 '../Stable/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Stable/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'

set size 0.5, 1
p '../Stable/Envelope15.dat' u 1:4 w l t 'Magnitude', \
 '../Stable/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Stable/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'

set key at 0, 0.8
unset ytics
unset xtics
unset border
unset xl
set size 1, 0.1
set yr [0:0.01]

p 2 t 'Magnitude', \
2 dt 5 lc 7 t 'Real', \
2 dt 4 t 'Imaginary'
\end{gnuplot}
\caption{Wave is stable for $b = 1.5$.}
\label{fig:stable}
\end{subfigure} \\
\vspace{4mm}
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
set grid
set key above
set xr [-2:2]
set yr [-0.75:0.75]
set xl '$T$'
set xtics 1

unset key
set multiplot layout 1, 2

set size 0.5, 1
p '../Break/Envelope8.dat' u 1:4 w l t 'Magnitude', \
 '../Break/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Break/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'

set size 0.5, 1
p '../Break/Envelope15.dat' u 1:4 w l t 'Magnitude', \
 '../Break/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Break/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'

set key at 0, 0.8
unset ytics
unset xtics
unset border
unset xl
set size 1, 0.1
set yr [0:0.01]
p 2 t 'Magnitude', \
2 dt 5 lc 7 t 'Real', \
2 dt 4 t 'Imaginary'

\end{gnuplot}
\caption{Wave breaks for $b = 1.4$.}
\label{fig:break}
\end{subfigure}
\caption{Simulation with $s = 0.11$, $a = 30$, $h = 0.6$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$. \textbf{Left:} Pulse after 8 iterations. \textbf{Right:} Pulse after 15 iterations.}
\label{fig:envelope}
\end{figure}

>>>>

\begin{figure*}[htbp]
\centering
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
set grid
set xr [-2:2]
set xl '$T$'
set xtics 0.5
set ytics 1
set yl '$|A|^2$ (AU)'

p '../Stable/Envelope25.dat' u 1:(10**3*$4**2) w l t 'Stable', \
'../Break/Envelope25.dat' u 1:(10**3*$4**2) w l dt 5 t 'Broken'
\end{gnuplot}
\caption{Envelope}
\label{fig:envelope}
\end{subfigure} \\

\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
set grid
set xl '$\omega$'
set yl '$|\widehat{A}|$'
set xr [-40:40]
set ytics 3

p '../Stable/Envelope25.dat' u 6:($7**2) w l t 'Stable', \
'../Break/Envelope25.dat' u 6:($7**2) w l dt 5 t 'Broken'

\end{gnuplot}
\caption{Fourier Transform}
\label{fig:fourier}
\end{subfigure} \\

\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
#d2(x,y) = ($0 == 0) ? (x1 = x, y1 = y, 1/0) : (x2 = x1, x1 = x, y2 = y1, y1 = y, if (x1 > x2 + pi) (x2 = x2 + 2 * pi), (y1-y2)/(x1-x2))

x0=NaN
y0=NaN

d(x,y) = (dx=x-x0, x0=x, dy=y-y0, y0=y, (dy > pi) ? (dy = dy-2*pi) : (dy), ((dy < -pi)) ? (dy = dy+2*pi) : (dy), dy/dx)

set grid
set xr [-2:2]
set yr [-20:20]
set xl '$T$'
set xtics 0.5
set ytics 10
set yl '$-\diff{\varphi}{T}$'
set key bottom right opaque

p '../Stable/Envelope25.dat' u 1:(-d($1,$5)) w l t 'Stable', \
'../Break/Envelope25.dat' u 1:(-d($1,$5)) w l dt 5 t 'Broken'
\end{gnuplot}
\caption{Chirp}
\label{fig:chirp}
\end{subfigure}

\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$. $\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton. In the stable case $b = 1.32$, whereas for the broken case $b = 1.25$. The pulse is shown after 25 iterations.}
\label{fig:pulse}
\end{figure*}

### 2018-12-15 Paper/Paper.tex
Updated paper

\section{Results}
\begin{wrapfigure}{r}{0.45\textwidth}
\vspace{-11mm}
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
f(x) = m * x + c
fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
set grid
set ytics 0.1
set xl '$s$'
set yl '$\zeta(s, 0)$'
set yr [0.75:1.05]
plot '../Zeta.dat' u 1:2 w l t 'Data', \
exp(f(x)) dt 4 t 'Fit'
\end{gnuplot}
\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
\label{fig:zeta}
\end{wrapfigure}
The model described is solved numerically, and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex. To gain some insight into this process we first consider a linear analysis that ignores the nonlinear fibre effects.

@@

Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
\begin{align*}
	|A_0| = \sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2},
\end{align*}
after passing through the gain and loss pieces, and having neglected the fibre nonlinearity, the envelope will have the form
\begin{align*}
	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
\end{align*}
where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
\begin{align}
\label{linear1}
	|A| = \sqrt{P} g(E) h \zeta(s, 0) \textrm{e}^{-T^2 / 2 \tilde{\sigma}^2}
\end{align}
where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. However, since dispersion conserves energy
\begin{align*}
	\int_{-\infty}^{\infty} P g(E)^2 h^2 \textrm{e}^{-T^2 / \sigma^2} \, \df T = 
	\int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, 0) \textrm{e}^{-T^2 / \widetilde{\sigma}^2} \, \df T,
\end{align*}
which reduces to $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
\begin{align*}
	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} \right).
\end{align*}
Finally, the pulse is modulated and so that after one loop the total effect is given by
\begin{align}
\label{linear2}
	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right).
\end{align}

In equilibrium, the envelope of the pulse is unchanged after completing a full circuit, in other words,
\begin{align*}
	\sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2} = 
	\sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right),
\end{align*}
or more explicitly,
\begin{align}
\label{eq:energycond}
	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta(s, 0) &= 1,&
	-\frac{T^2}{2 \sigma^2} &= -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2}.
\end{align}
The second condition simplifies to
\begin{align*}
	\sigma = \sqrt{1 - \zeta^4(s, 0)}
\end{align*}
and the peak of the pulse can be found by integration to give
\begin{align*}
	P = \frac{E}{\sqrt{\pi} \sigma}.
\end{align*}
Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
\begin{align}
	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
	\label{eq:equilenergy}
\end{align}

@@

In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive. However, this is not necessarily the case with the inclusion of the nonlinearity. The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations. These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled. \\

@@

\begin{figure}[!bp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
load '/home/brady/Templates/Blues.p'
set grid
set xl '$s$'
set yl '$b$'
set cbl '$E \, (\times 10^3)$'
set view map
set cbr [0:4]
sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
'EnergyContours.dat' w l lc 'black' lw 0.5 not
\end{gnuplot}
\caption{Energy as a function of $s$ and $b$. The energy is constant along the black lines. Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
\label{fig:energy}
\end{figure}

>>>>

\section{Results}
%\begin{wrapfigure}{r}{0.45\textwidth}
%\vspace{-11mm}
%\centering
%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
%f(x) = m * x + c
%fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
%set grid
%set ytics 0.1
%set xl '$s$'
%set yl '$\zeta(s, 0)$'
%set yr [0.75:1.05]
%plot '../Zeta.dat' u 1:2 w l t 'Data', \
%exp(f(x)) dt 4 t 'Fit'
%\end{gnuplot}
%\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
%\label{fig:zeta}
%\end{wrapfigure}
The linear version of the model described can be solved analytically , however, the full non-linear version must be solved numerically. Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex. To gain some insight into this process we first consider the linear analysis that ignores the nonlinear fibre effects.

@@

Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
\begin{align*}
	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),
\end{align*}
where $C$ is the chirp. After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
\begin{align*}
	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),&
	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
\end{align*}
is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread \cite{agrawal2013}. This can be written as
\begin{align}
\label{linear1}
	A_3 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
\end{align}
where $\widetilde{\sigma}^2$ is the resulting variance, and $\widetilde{C}$ is the resulting chirp. Finally, the pulse is modulated---after one loop the total effect is given by
\begin{align}
\label{linear2}
	A_4 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
\end{align}

In equilibrium, the envelope of the pulse as well as the chirp are unchanged after completing a full circuit, it must bet that $A_0 = A_4$.
%\begin{align*}
%	\sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) = 
%	\sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
%\end{align*}
More explicitly, this gives three conditions:
\begin{align}
\label{eq:energycond}
	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \qquad
	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
	\frac{C}{\sigma^2} = \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
\end{align}
The out-coming variance and chirp are given by \cite{agrawal2013}
\begin{align}
\label{eq:tildes}
	\widetilde{\sigma}^2 = \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \qquad
	\widetilde{C} = C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
\end{align}
From \eqref{eq:energycond} and \eqref{eq:tildes} we find that the equilibrium variance reduces to the quartic
\begin{align*}
\left( \sigma^2 \right)^4 + 4 s^2 \left( \sigma^2 \right)^3 - 20 s^2 \left( \sigma^2 \right)^2 + 32 s^2 \left( \sigma^2 \right) - 16 s^2 = 0,
\end{align*}
which has the solution
\begin{align*}
\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
\end{align*}
Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
\begin{align}
	\label{eq:equilenergy}
	E = \frac{h^2 \zeta}{1 - h^2 \zeta} \ln \left( a h^2 \zeta \right),
\end{align}
by letting $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.

@@

In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive. However, this is not necessarily the case with the inclusion of the nonlinearity. The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations. These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled. \\

@@

\begin{figure}[!bp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
load '/home/brady/Templates/Blues.p'
set grid
set xl '$s$'
set yl '$b$'
set cbl '$E \, (\times 10^{-3})$'
set view map
set cbr [0:4]
sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
'EnergyContours.dat' w l lc 'black' lw 0.5 not
\end{gnuplot}
\caption{Energy as a function of $s$ and $b$. The energy is constant along the black lines. Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
\label{fig:energy}
\end{figure}
